Mental Well-Being

### 2023-01-17 docsrc/documentation/notebooks/mental_well_being.Rmd
get all current module templates with better formatting in taskbar.

# Mental Well-Being

@@

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

## References

>>>>

## Mental Well-Being

@@

```{r neighbourhood_barchart, echo=FALSE}
continuous_density("SF_12")
```
### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
ols_histogram("../../../data/transitions/test/sf12_ols_2018_2019.rds", "y")
ols_output("../../../data/transitions/test/sf12_ols_2018_2019.rds")
```

### References
